---
title: "Flint"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
```

## Monster Bits

### Lizard
```{r}
lizard = 195
```


### Spider (mwindaji)
```{r}
spider = 135
```

### Small crocks
```{r}
baby_crock = 90 
```

### Big crock
 - resistances 
 - electricity damage
```{r}
big_crock = 90
```



### Spending
Lizard Leather Armor (Level 5)
+2 ac, +4 dex cap, -1 check penalty
```{r}
lizard = lizard - 2 # base armor
lizard = lizard - 160 # level 5 upgrade
```





Yusuf's shield

Hardness 7 HP 34, BT 17
```{r}
big_crock = big_crock - 1 # base cost
baby_crock = baby_crock - 60 # refinement level 4
baby_crock = baby_crock - 30 # level 3 sturdy imbuement
big_crock = big_crock - 5 # level 3 sturdy imbuement
```


Flint's buckler

Hardness 4, HP 20, BT 10
```{r}
big_crock = big_crock - 1 # base cost
big_crock = big_crock - 60 # level 4 refinement
big_crock = big_crock - 20 # level 2 sturdy imbuement
```


Shocking bow 
```{r}
lizard = lizard - 3 # base cost
spider = spider - 100 # level 4 refinement

```


Consumables

```{r}
lizard = lizard - 16 # Chameleon Suit
lizard = lizard - 3 # owlbear claw
```

Totals

```{r}
big_crock
baby_crock
spider
lizard
```

## Other Spending



```{r}
# starting
gold = 450


gold = gold - 
    60 - #crafter's eyepiece
    100 - # sleeves of storage
    30 - # hand of the mage
    3 - # shortbow
    35 - # potency rune
    65 - # striking rune
    5 - # healer's tools
    2 - # repair kit
    1 - # buckler
    1 - # buckler number 2
    1 - # spare buckler
    0.4 - # winter clothes
    30 - # hat of disguise
    1 -# climbing kits 2
    3 - # impact foam chassis
    3 - # blast boots
    3 - # clockwork goggles
    20 -  # spyglass
    4  - # 10 rations
    1.5 # adventurer kit

# formulae
# all sub level 6 gadgets
gold = gold - 
     0.5*8 - # 8 level 1 items
    1*5 - # 5 level 2 items
    1.5*5 - # 5 level 3 items
    2.5*4 - # 4 level 4 items
    4*3 - # 3 level 5 items
    6.5*2 + # 2 level 6 items
    6.5*2 + 4 # 3 free formulas from gadget specialist



```

### Formulae

- All, common+uncommon gadgets less than level 6
- Shining Ammunition
- crying angel pendant
- owlbear claw
- 



### Inventory

### Gear

- buckler
- repair kit
- healing kit
- sleeves of storage
- 2 bucklers
- winter clothes
- 2 climbing kits
- spyglass
- 10 rations

### Magic items

- +1 striking shortbow
- +1 lizard skin leather armor
- crafter's eyepiece
- hat of disguise
- hand of the mage
- owlbear claw talisman


### Gadgets

- Impact foam chassis (lesser)
- Chameleon Suit
- blast boots (lesser)
- clockwork goggles (lesser)


## Notes

Patiently waiting: racist ass
oakbloom by the wind: apparently non racist mom
eye above all: old bird dude


### Codes

Repair heal = 15

Unstable damage = 6

```{r}
library(diceSyntax)
roll('6d6') # explode

# Unstable DC
roll("1d20") %>% 
    {ifelse(.>= 17,yes = "Success",no = ifelse(.>=7 ,yes = 'Failure',no= 'Crit Fail'))} 


# Trained healing
roll("1d20+12") %>% 
    {ifelse(.>= 15,yes = "Success",no = ifelse(.>=5 ,yes = 'Failure',no= 'Crit Fail'))}

roll('2d8') # success
roll('4d6') # crit success

# Expert healing
roll("1d20+12") %>% 
    {ifelse(.>= 20,yes = "Success",no = ifelse(.>=10 ,yes = 'Failure',no= 'Crit Fail'))}

roll('2d8+10') # success
roll('4d8+10') # crit success
 
```


### travel

serpent's head rock
canyon submerged 
stone whirl 
ribbons
eventual tribe meeting, take winter supplies

ancestor stones
walk carefully
great horizon
hanging giant
tunnels in the mountains
bashkani


