---
title: "Flint"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
```

## Monster Bits

### Lizard
```{r}
lizard = 195
```


### Spider (mwindaji)
```{r}
spider = 135
```


### Spending
Lizard Leather Armor (Level 5)
+2 ac, +4 dex cap, -1 check penalty
```{r}
lizard = lizard - 2 # base armor
lizard = lizard - 160 # level 5 upgrade
```


Chameleon Suit
```{r}
lizard = lizard - 16
```


Totals

```{r}
spider
lizard
```

## Other Spending



```{r}
# starting
gold = 450


gold = gold - 
    60 - #crafter's eyepiece
    100 - # sleeves of storage
    3 - # shortbow
    35 - # potency rune
    65 - # striking rune
    5 - # healer's tools
    2 - # repair kit
    1 - # buckler
    1 - # buckler number 2
    1 - # spare buckler
    0.4 - # winter clothes
    30 - # hat of disguise
    1 -# climbing kits 2
    20 # spyglass

```

### Recipes

```{r}


```

### Inventory

+1 striking shortbow
+1 lizard skin leather armor
buckler
repair kit
healing kit
sleeves of storage
crafter's eyepiece
2 bucklers
winter clothes
hat of disguise
2 climbing kits
spyglass

## Notes

Patiently waiting: racist ass
oakbloom by the wind: apparently non racist mom
eye above all: old bird dude



### travel

serpent's head rock
canyon submerged 
stone whirl 
ribbons
eventual tribe meeting, take winter supplies

ancestor stones
walk carefully
great horizon
hanging giant
tunnels in the mountains
bashkani


