---
title: "Katip AL logsheet"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
add = function(array, things){
    array_name = substitute(array)
    array_name = as.character(array_name)
    array = c(array, things)
    assign(array_name,array,parent.frame())
}

remove = function(array,things){
    array_name = substitute(array)
    array_name = as.character(array_name)
    
    for (x in things){
        m = match(x,array)
        assertthat::assert_that(!is.na(m))
        array = array[-match(x,array)]
    }
    
    assign(array_name,array,parent.frame())
}

# spell add template
# add(spell_book,
#     spells[names(spells) %in% 
#                c('')])
```

### On creation

```{r}

library(wizaRd)

level = 1
gold = 15
downtime = 0
magic_items = c()
consumables = c()
common_items = c()
spell_book = list();class(spell_book) = append(class(spell_book),'spellList')


# cantrips
add(spell_book,
    spells[names(spells) %in% 
               c("Mage Hand", # telekinetic
                 "Minor Illusion", # magic initiate
                 "Prestidigitation", # magic initiate
                 "Mind Sliver", # wizard starting
                 "Fire Bolt",
                 "Mold Earth")])


add(spell_book,
    spells[names(spells) %in% 
               c('Magic Missile',
                 "Absorb Elements",
                 "Fog Cloud",
                 "Feather Fall",
                 "Mage Armor",
                 "Catapult",
                 "Shield" # magic initiate
               )])
```

### Adventures 

####  Adventure: DDEX2-6 Breath of the Yellow Rose (Tier 1)

```{r}
level = level + 1
downtime = downtime + 10
gold = gold + 100
add(magic_items, "Ring of Mind Shielding")
add(consumables,"Scroll of Misty Step")
```

#### Steamy Shores of Danger (CCC-CIC-09)

```{r}
level = level + 1
downtime = downtime + 10
gold = gold + 100
add(magic_items,'Geyser Figurine (Decanter of Endless Water)')
add(consumables,c("Potion of Healing","Scroll of Protection from Evil and Good"))
```

You have learned how to introduce yourself in a formal and impressive way. During your future encounters with members of tribal cultures of Big Folk Island or the village of Jarko’tu’ta you may gain advantage on social checks if you recite your Greeting during introductions (DM discretion).
The greeting of the forefathers is simple and consists of 7 parts:
- Part 1: Name of character
- Part 2: Name of father
- Part 3: Name of grandfather
- Part 4: Name of great grandfather
- Parts 5, 6, 7: Life accomplishments

### Downtime

#### Copy misty step

```{r}
gold = gold - 100
downtime = downtime - 1
add(spell_book,
    spells[names(spells) %in% c('Misty Step')])
remove(consumables,'Scroll of Misty Step')
```


#### Copy protection from evil and good

```{r}
gold = gold - 50
downtime = downtime - 1
add(spell_book,
    spells[names(spells) %in% c('Protection from Evil and Good')])
remove(consumables, "Scroll of Protection from Evil and Good")
```

#### Scribe scroll of fog cloud
```{r}
gold = gold - 25
downtime = downtime - 1
add(consumables,"Scroll of Fog Cloud")
```

#### Scribe scroll of protection from good and evil
```{r}
gold = gold - 25
downtime = downtime - 1
add(consumables,"Scroll of Protection From Good and Evil")
```
### Shopping
```{r}
gold = gold - 
  1 - # caltrops
  1 - # ball bearings
  2 - # crowbar
  2 - # manacles
  0.5 -  # 10 pitons
  1 - # 50 ft rope
  5 - # mirror
  0.05 - # signal whistle
  1 - #  oil x 5
  0.5 # lamp
```
### Level ups

#### 1->2

```{r}
add(spell_book,
    spells[names(spells) %in% 
               c('Identify',"Unseen Servant")])
```

#### 2->3

```{r}
add(spell_book,
    spells[names(spells) %in% 
               c('Phantasmal Force',"Dragon's Breath")])
```

### Final State
```{r}
c(level = level,
  gold = gold,
  downtime = downtime)
magic_items
common_items
consumables
spell_book
```
