---
title: "Katip AL logsheet"
output: github_document
---

### Contents

* [On creation](#on-creation)
* [Adventures](#adventures)
* [Downtime](#downtime)
* [Shopping](#shopping)
* [Level ups](#level-ups)
* [Final State](#final-state)


```{r setup, include=FALSE}
library(wizaRd)
library(magrittr)

knitr::opts_chunk$set(echo = TRUE)
add = function(array, things){
    array_name = substitute(array)
    array_name = as.character(array_name)
    array = c(array, things)
    assign(array_name,array,parent.frame())
}

remove = function(array,things){
    array_name = substitute(array)
    array_name = as.character(array_name)
    
    for (x in things){
        m = match(x,array)
        assertthat::assert_that(!is.na(m))
        array = array[-match(x,array)]
    }
    
    assign(array_name,array,parent.frame())
}

# spell add template
# add(spell_book,
#     spells[names(spells) %in% 
#                c('')])
```

### On creation

```{r}


level = 1
gold = 15
downtime = 0
magic_items = c()
consumables = c()
common_items = c()
mundane_items = c()
spell_book = list();class(spell_book) = append(class(spell_book),'spellList')

add(mundane_items,
    c('dagger','arcane focus','spellbook','bottle of black ink','quill','small knife','letter','set of common clothes','belt pouch','backpack','bedroll','mess kit','tinderbox','10 torches','10 days of rations','waterskin',"50 ft hempen rope"))


# cantrips
add(spell_book,
    spells[names(spells) %in% 
               c("Mage Hand", # telekinetic
                 "Minor Illusion", # magic initiate
                 "Prestidigitation", # magic initiate
                 "Mind Sliver", # wizard starting
                 "Fire Bolt",
                 "Mold Earth")])


add(spell_book,
    spells[names(spells) %in% 
               c('Magic Missile',
                 "Absorb Elements",
                 "Fog Cloud",
                 "Feather Fall",
                 "Mage Armor", # magic initiate
                 "Catapult",
                 "Shield"
               )])
```

### Adventure rewards

####  Adventure: DDEX2-6 Breath of the Yellow Rose (Tier 1)

```{r}
level = level + 1
downtime = downtime + 10
gold = gold + 100
add(magic_items, "Ring of Mind Shielding")
add(consumables,"Scroll of Misty Step")
```

#### Steamy Shores of Danger (CCC-CIC-09)

```{r}
level = level + 1
downtime = downtime + 10
gold = gold + 100
add(magic_items,'Geyser Figurine (Decanter of Endless Water)')
add(consumables,c("Potion of Healing","Scroll of Protection from Evil and Good"))
```

You have learned how to introduce yourself in a formal and impressive way. During your future encounters with members of tribal cultures of Big Folk Island or the village of Jarko’tu’ta you may gain advantage on social checks if you recite your Greeting during introductions (DM discretion).
The greeting of the forefathers is simple and consists of 7 parts:
- Part 1: Name of character
- Part 2: Name of father
- Part 3: Name of grandfather
- Part 4: Name of great grandfather
- Parts 5, 6, 7: Life accomplishments

#### The Donjon (Tier 1)

```{r}
level = level + 1
downtime = downtime + 10
gold = gold + 166
add(magic_items,"Goggles of the Night")

```

### Downtime

#### Copy misty step

```{r}
gold = gold - 100
downtime = downtime - 1
add(spell_book,
    spells[names(spells) %in% c('Misty Step')])
remove(consumables,'Scroll of Misty Step')
```


#### Copy protection from evil and good

```{r}
gold = gold - 50
downtime = downtime - 1
add(spell_book,
    spells[names(spells) %in% c('Protection from Evil and Good')])
remove(consumables, "Scroll of Protection from Evil and Good")
```

#### Scribe scroll of fog cloud
```{r}
gold = gold - 25
downtime = downtime - 1
add(consumables,"Scroll of Fog Cloud")
```

#### Scribe scroll of protection from good and evil
```{r}
gold = gold - 25
downtime = downtime - 1
add(consumables,"Scroll of Protection From Good and Evil")

gold = gold - 50
downtime = downtime - 2
add(consumables,c("Scroll of Protection From Good and Evil","Scroll of Protection From Good and Evil"))
```


#### Scribe scroll of magic missile
```{r}
gold = gold - 50
downtime = downtime - 2

add(consumables,c("Scroll of Magic Missile","Scroll of Magic Missile"))

```
### Shopping
```{r}
gold = gold - 
  1 - # caltrops
  1 - # ball bearings
  2 - # crowbar
  2 - # manacles
  0.5 -  # 10 pitons
  5 - # mirror
  0.05 - # signal whistle
  1 - #  oil x 5
  0.5 - # lamp
  1 # 5 more oil. one used

add(mundane_items,
    c('caltrops','ball bearings','crowbar','manacles','10 pitons','mirror','signal whistle','9 oil','lamp'))

```

### Adventure Item use

#### The Donjon (Tier 1)

```{r}
gold = gold - 1
remove(consumables,"Scroll of Protection From Good and Evil")
# flask of oil

```

### Level ups

#### 1->2

```{r}
add(spell_book,
    spells[names(spells) %in% 
               c('Identify',"Unseen Servant")])
```

#### 2->3

```{r}
add(spell_book,
    spells[names(spells) %in% 
               c('Phantasmal Force',"Dragon's Breath")])
```


#### 3-> 4
```{r}
add(spell_book,
    spells[names(spells) %in% 
               c('Detect Magic','Alter Self',"Mending")])
```
### Final State
```{r}
c(level = level,
  gold = gold,
  downtime = downtime)
magic_items %>% sort
common_items %>% sort
consumables %>% sort
mundane_items %>% sort
spell_book
```
