---
title: "Katip_dndone_chrono"
output: github_document
---

### Contents

* [On creation](#on-creation)
* [Level ups](#level-ups)
* [Timeline](#timeline)
* [Final State](#final-state)



```{r setup, include=FALSE}
# https://5e.tools/tables.html#scribing%20spell%20scrolls%3b%20spell%20scroll%20costs_xphb
# scribing costs/ purchase cost is double
library(wizaRd)
library(magrittr)

scribe_p = list(`0` = 15, `1` = 25, `2`= 100, `3` = 150,`4` = 1000, `5` = 1500, `6` = 10000,
                `7` = 12500, `8` =15000, `9` = 50000)
scroll_p = scribe_p %>% lapply(\(x){x*2})

# buy_and_copy = function(name,level,spell_book,downtime,gold){
#     book_name = substitute(spell_book) 
#     dt_name = substitute(downtime)
#     gp_name = substitute(gold)
#     
#     if(name %in% names(spell_book)){
#         stop("Trying to relearn known spell")
#     }
#     
#     # costs for a scribe wizard
#     dt_cost = ifelse(level<=4, .1,.2)
#     
# }
# 
# copy_scroll = function(name,level,spell_book,downtime,gold,consumables){
#     
# }


knitr::opts_chunk$set(echo = TRUE)
add = function(array, things){
    array_name = substitute(array)
    array_name = as.character(array_name)
    array = c(array, things)
    assign(array_name,array,parent.frame())
}

remove = function(array,things){
    array_name = substitute(array)
    array_name = as.character(array_name)
    for (x in things){
        m = match(tolower(x),tolower(array))
        assertthat::assert_that(!is.na(m))
        array = array[-match(tolower(x),tolower(array))]
    }
    
    assign(array_name,array,parent.frame())
}

alter_count = function(array,thing,count){
    array_name = substitute(array)
    array_name = as.character(array_name)
    
    target = array[grepl(thing,array,ignore.case = TRUE)]
    assertthat::assert_that(length(target)==1 || length(target)==0)
    
    if(length(target)==0){
        assertthat::assert_that(count>0)
        array = c(array,paste(count,thing))
    } else{
        old_count = stringr::str_extract(target,'^[0-9]+') %>% as.integer()
        if(!is.na(old_count)){
            new_count = old_count + count
            assertthat::assert_that(new_count>=0)
            if(new_count>0){
                array[grepl(thing,array,ignore.case = TRUE)] = gsub("[0-9]+",new_count,target)
            } else{
                array = array[!grepl(thing,array,ignore.case = TRUE)]
            }
        } else {
            assertthat::assert_that(count>0)
            array[grepl(thing,array,ignore.case = TRUE)] = paste(count, target)
        }
    }
    
    assign(array_name,array,parent.frame())
}

ab_cost = function(score){
    cost = score-8
    cost = cost + max(score- 13,0)
    return(cost)
}

available_elements = function(spell_book){
    damage_types = c('acid','bludgeoning',
                     'cold','fire','force','lightning',
                     'necrotic','percing','poison','psychic','radiant',
                     'slashing','thunder')
    
    lapply(1:9,\(x){
        level_spells = spell_book %>% wizaRd::filterSpells(level = x)
        spell_text = level_spells %>% purrr::map_chr('text')
        damage_types %>% sapply(\(y){
            any(grepl(paste0("\\b",y,"\\b"),spell_text,ignore.case = TRUE))
        }) %>% which %>% names
        
    })->elements
    names(elements) = 1:9
    
    return(elements %>% 
               {.[sapply(.,length)!=0]})
}

stat_mod = function(stat){
    floor((stat-10)/2)
}

# spell add template
# add(spell_book,
#       spells[names(spells) %in% 
#               c('')])
```


### On creation

```{r}
level = 1
proficiency = 2
downtime = 0
gold = 0
hp = 0 
prepare_limit = 0
ability_scores = c(Str=0,Dex=0,Con=0,Int=0,Wis=0,Cha=0)
feats = c()
features = c()
skills = c()
expertise = c()
tools = c()
magic_items = c()
consumables = c()
common_items = c()
mundane_items = c()
spell_book = list();class(spell_book) = append(class(spell_book),'spellList')
```

#### Class - Wizard

```{r}
add(skills,c("Insight","Investigation"))
add(mundane_items, c("2 daggers","Quarterstaff","Robe","Spellbook",
                     "backpack","book","ink","ink pen","lamp","10 flasks of oil",
                     "10 sheets of parchment","tinderbox"))


# 3 cantrips can be changed at long rest
add(spell_book,
    spells[names(spells) %in% 
               c("Mind Sliver",
                 "Fire Bolt",
                 "Toll the Dead")])

# 6 level 1 spells
add(spell_book,
    spells[names(spells) %in% 
               c("Magic Missile", # scribed
                 "Absorb Elements",
                 "Fog Cloud", # scribed
                 "Feather Fall",
                 "Catapult",
                 "Shield")])


add(features,"Ritual Adept")
add(features,"Arcane Recovery: Half level")
```
#### Background - DMG custom

```{r}
add(feats, "Magic Initiate(wizard)")
# magic initiate cantrips
add(spell_book,
    spells[names(spells) %in% 
               c("True Strike",
                 "Minor Illusion")])
# magic initiate lvl1 spell,
add(spell_book,
    spells[names(spells) %in% 
               "Mage Armor"])
add(features,"Daily mage armor from magic initiate")


add(skills, c("Arcana","Persuasion"))
add(tools, "Thieves' tools")
gold = gold+50
```


#### Species - Human
```{r}
add(features,"Resourceful: inspiration per long rest")
# skillful
add(skills,'Perception')
# versatile
add(feats,"Skilled")
add(skills,c("Stealth","Acrobatics","Deception"))

```

#### Languages

```{r}
languages = c('common','common sign language','elvish')
```

#### Ability scores

```{r}
# point buy
ability_scores = c(Str = 8,
                   Dex = 14, 
                   Con = 13, 
                   Int = 15, 
                   Wis = 12, 
                   Cha = 10 
)
# 27 check
costs = ability_scores %>% sapply(ab_cost) %>% sum
assertthat::assert_that(costs == 27)

# custom background
ability_scores['Int'] = ability_scores['Int'] + 2
ability_scores['Con'] = ability_scores['Con'] + 1

# hp
hp = 6+stat_mod(ability_scores['Con'])
```



#### Starting equipment


```{r}

gold = gold -
    1 - # caltrops
    1 - # ball bearings
    2 - # crowbar
    2 - # manacles
    5 - # mirror
    0.05 - # signal whistle
    25 - # thieves' tools
    2 - # 4 days of rations
    1 - # rope
    .2 - # waterskin
    2 # 4 javelins

add(mundane_items,
    c('caltrops','ball bearings','crowbar','manacles','mirror','signal whistle',"thieves' tools","rope","waterskin","4 days of rations"))

alter_count(mundane_items,"javelin",2)
```



### Level ups

#### Level 2

```{r}
hp = hp + 4+stat_mod(ability_scores['Con'])
add(expertise,"Investigation")
add(spell_book,
    spells[names(spells) %in% 
               c('Identify',"Find Familiar")])
```

#### Level 3

```{r}
hp = hp + 4+stat_mod(ability_scores['Con'])
add(features,c('Wizardly Quill: quick spell copying, quick erase as a bonus action','Awakened Spellbook:replace damage type, 1 quick ritual per long rest'))
add(spell_book,
    spells[names(spells) %in% 
               c('Phantasmal Force',"Dragon's Breath")])
```

#### Level 4
```{r}
hp = hp + 4+stat_mod(ability_scores['Con'])
add(feats,"Telekinetic")
add(features,"Telekinetic: bonus action shove 5 feet, str save, spell DC, +30 feet range to mage hand")
ability_scores['Int'] = ability_scores['Int'] + 1
add(spell_book,
    spells[names(spells) %in% 
               "Mage Hand"])



add(spell_book,
    spells[names(spells) %in% 
               c('Suggestion','Alter Self',"Mending")])
```

#### Level 5

```{r}
hp = hp + 4+stat_mod(ability_scores['Con'])
add(features, "Memorize spell: Replace one prepared spell on short rest")
add(spell_book,
    spells[names(spells) %in% 
               c('Glyph of Warding','Fireball')])
add(magic_items,"Arcane Grimoire +1 (UC)")
```

#### Level 6

```{r}
hp = hp + 4+stat_mod(ability_scores['Con'])

add(features, "Manifest mind: bonus action to manifest, 60 feet range. light in a 10-foot radius, darkvision with a range of 60 feet, free audio vis share, Prof bonus times spell casting. 300 feet max distance")

add(spell_book,
    spells[names(spells) %in% 
               c('Counterspell','Summon Undead')])
# don't think stat block elemnts count as damage types
spell_book$`Summon Undead`$text = ""

# summon undead
gold = gold - 300
add(mundane_items,"Gilded Skull 300 gp")

```

#### Level 7
```{r}
hp = hp + 4+stat_mod(ability_scores['Con'])
add(spell_book,
    spells[names(spells) %in% 
               c('Elemental Bane',"Raulothim's Psychic Lance")])
```

#### Level 8

```{r}
hp = hp + 4+stat_mod(ability_scores['Con'])
ability_scores['Int'] = ability_scores['Int'] + 2
add(spell_book,
    spells[names(spells) %in% 
               c('Banishment',"Dimension Door")])
```

### Timeline


#### Adventure: DDEX2-6 Breath of the Yellow Rose (Tier 1)

```{r}
level = level + 1
downtime = downtime + 10
gold = gold + 100
add(magic_items, "Ring of Mind Shielding (UC)")
alter_count(consumables,"Scroll of Misty Step",1)
```

#### Downtime: Copy scroll of misty step

```{r}
gold = gold - 100
downtime = downtime - 1
add(spell_book,
    spells[names(spells) %in% c('Misty Step')])
alter_count(consumables,'Scroll of Misty Step',-1)
```


#### Adventure: Steamy Shores of Danger (CCC-CIC-09)

```{r}
level = level + 1
downtime = downtime + 10
gold = gold + 100
add(magic_items,'Geyser Figurine (Decanter of Endless Water) (UC)')
alter_count(consumables,"Potion of Healing",1)
alter_count(consumables,"Scroll of Protection from Evil and Good",1)
```

You have learned how to introduce yourself in a formal and impressive way. During your future encounters with members of tribal cultures of Big Folk Island or the village of Jarko’tu’ta you may gain advantage on social checks if you recite your Greeting during introductions (DM discretion).
The greeting of the forefathers is simple and consists of 7 parts:
- Part 1: Name of character
- Part 2: Name of father
- Part 3: Name of grandfather
- Part 4: Name of great grandfather
- Parts 5, 6, 7: Life accomplishments


#### Downtime: Copy protection from evil and good

```{r}
gold = gold - 50
downtime = downtime - 1
add(spell_book,
    spells[names(spells) %in% c('Protection from Evil and Good')])
alter_count(consumables,"Scroll of Protection from Evil and Good",-1)
```

#### Downtime: Scribe scroll of fog cloud
```{r}
gold = gold - 25
downtime = downtime - 1
alter_count(consumables,"Scroll of Fog Cloud",1)
```


#### Downtime: Scribe scroll of protection from evil and good
```{r}
gold = gold - 25
downtime = downtime - 1
alter_count(consumables,"Scroll of Protection from Evil and Good",1)
```


#### Adventure: The Donjon (Tier 1)

 
```{r}
gold = gold - 1
alter_count(consumables,"Scroll of Protection From Evil and Good",-1)
alter_count(mundane_items,"flasks of oil",-1)
```

```{r}
level = level + 1
downtime = downtime + 10
gold = gold + 166
add(magic_items,"Goggles of the Night (UC)")
```




#### Adventure: CCC-TRI-06 Haggard Heroes

There's a bit of a chronological silliness and a lost adventure here but it evens out with the next adventure
```{r}
downtime = downtime +10
gold = gold + 2000
alter_count(consumables, "Potion of fire breath",1)
add(magic_items, "+1 half plate (R)")
```

#### 2024 rules switch

#### Adventure DDAL04-06 The Ghost (Tier 1)
```{r}
alter_count(consumables,"Potion of Healing",-1)
```


```{r}
level = level +1
downtime = downtime + 10
gold = gold + 96
add(magic_items,"Boots of Elvenkind (UC)")
alter_count(mundane_items,"Antitoxin",1)
alter_count(consumables,"Potion of Greater Healing",1)
alter_count(consumables,"Potion of Cold Resistence",1)
alter_count(consumables,"Scroll of Detect Thoughts",1)
```


#### Downtime: Shopping

```{r}
gold = gold - 100
alter_count(mundane_items,'pearl 100 gp',1) # identify spell component

gold = gold - 200
alter_count(consumables,'Potion of Greater Healing',1)

gold = gold -10 # find familiar casting

```

#### Downtime: Scroll buying and copying

```{r}
gold = gold - 50 - 50
downtime = downtime - 1
add(spell_book,
    spells[names(spells) %in% c('Detect Magic')])

gold = gold - 300 -150
downtime = downtime -.1
add(spell_book,
    spells[names(spells) %in% c('Haste')])


gold = gold - 100
alter_count(consumables,"Scroll of Detect Thoughts",-1)
downtime = downtime -.1
add(spell_book,
    spells[names(spells) %in% c('Detect Thoughts')])


gold = gold - 300 - 150 
downtime = downtime -.1
add(spell_book,
    spells[names(spells) %in% c('Fly')])
```

#### Downtime: Scroll scribing
```{r}
gold = gold - 2*50 # 25 + 25 material cost
downtime = downtime - 2
alter_count(consumables,"Scroll of Protection from Evil and Good",2)

gold = gold - 100*1
downtime = downtime -3*1
alter_count(consumables,"Scroll of Alter Self",1)

gold = gold - 150*2
downtime = downtime - 5*2
alter_count(consumables,"Scroll of Haste",2)

gold = gold - 150
downtime = downtime - 5
alter_count(consumables,"Scroll of Fly",1)

gold = gold - 150
downtime = downtime - 5
alter_count(consumables,"Scroll of Fireball",1)

```


#### Adventure: DDEP07-02 Drums of the Dead

```{r}
alter_count(consumables,"Scroll of Protection From Evil and Good",-1)
alter_count(mundane_items,"flasks of oil",-1)
alter_count(consumables,"Scroll of Fireball",-1)
gold = gold -50
alter_count(consumables,"Potion of Healing",1)
```

Wand of Lightning Bolts
This slender glass wand is wrapped in a tight coil of thin copper wire. When used, the wielder’s hair stands up on end.

Ring of Evasion
This ring of dark wood drips thick, viscous oil that soaks through even the thickest gloves.

Mantle of Spell Resistance
Small, palm-sized mirrors have been sewn into the outside of this heavy woolen cloak. Occasionally, the mirrors reflect the image of a strange, bedraggled man in a black cloak looking back at those who view it.

Story Award:
Plague Buster. You helped an alliance of heroes concoct an antidote for the zombie plague ravaging Chult. Your exposure to the antidote has hardened your immune system against disease. You have advantage on saving throws made to resist disease.

```{r}
gold = gold + 700 
level = level + 1
downtime = downtime + 10
add(magic_items,"Wand of Lightning Bolts (R)")
add(magic_items,"Ring of Evasion (R)")
add(magic_items,"Mantle of Spell Resistance (R)")
add(features,"Plague Buster: Advantage on saving throws against disease")
```

#### Downtime: Trading Post

```{r}
remove(magic_items,"Geyser Figurine (Decanter of Endless Water) (UC)")
add(magic_items, "Gauntlets of Ogre Power (UC)")
```


#### Downtime: Buying and copying scroll of invisibility

```{r}
gold = gold - 200 - 100
dowtime = downtime -.1
add(spell_book,
    spells[names(spells) %in% c('Invisibility')])
```

#### Adventure: The Dungeon of Smelly Doom (WBW-DC-AMQ-05)

```{r}
gold = gold + 1000
downtime = downtime + 10
level = level + 1
add(magic_items,"Elven Chain Shirt (R)") # TM
add(common_items,"Pole of Collapsing")
alter_count(consumables,"Potion of Greater Healing",1)
alter_count(consumables,"Scroll of Dispel Magic",1)
alter_count(consumables,"Potion of Resistance (Poison)",1)
```

#### Downtime: Copy scroll of dispell magic

```{r}
dowtime = downtime -.1
gold = gold - 150
alter_count(consumables,"Scroll of Dispel Magic",-1)
add(spell_book,
    spells[names(spells) %in% c('Dispel Magic')])
```

#### Downtime: Buy copy scrolls
```{r}
gold = gold - 50- 50
downtime = downtime -.1
add(spell_book,
    spells[names(spells) %in% c('Comprehend Languages')])

```

#### Adventure: CCC-GHC-BK1-05 - For the Glory of Bloutar

```{r}
alter_count(consumables,"Potion of Healing",-1)
```

```{r}
downtime = downtime + 10
level = level + 1
gold = gold + 1250
alter_count(consumables,"Potion of Healing",1)
alter_count(consumables,"Potion of Climbing",1)
alter_count(consumables,"Scroll of Blink",1)
alter_count(consumables,"Scroll of Fabricate",1)
alter_count(consumables,"Scroll of Major Image",1)

add(magic_items,'Stout: Longsword +2 (R)')

```

#### Downtime: Copy scrolls

```{r}
downtime = downtime -.1
gold = gold - 150
alter_count(consumables,"Scroll of Blink",-1)


downtime = downtime -.1
gold = gold - 150
alter_count(consumables,"Scroll of Major Image",-1)

downtime = downtime -.1
gold = gold - 200
alter_count(consumables,"Scroll of Fabricate",-1)

add(spell_book,
    spells[names(spells) %in% c('Blink','Major Image','Fabricate')])
```

#### Downtime: Buy and copy scrolls

```{r}
gold = gold - scroll_p$`2` - 50*2
downtime = downtime -.1
# my list is out of date...
spells$`Spray of Cards` = list(text = "force",
                               level  =2,
                               name = 'Spray of Cards',
                               school = 'conjuration',
                               classes = c('wizard'),
                               source = "PHB",
                               range = "Self",
                               castingTime = '1 action',
                               components = c("V","S"))
add(spell_book,
    spells[names(spells) %in% "Spray of Cards"])

gold = gold - scroll_p$`2` - 50*2
downtime = downtime -.1
add(spell_book,
    spells[names(spells) %in% "Skywrite"])


gold = gold - scroll_p$`1` - 50
downtime = downtime -.1
add(spell_book,
    spells[names(spells) %in% "Alarm"])

gold = gold - scroll_p$`1` - 50
downtime = downtime -.1
add(spell_book,
    spells[names(spells) %in% "Tenser's Floating Disk"])

gold = gold - scroll_p$`1` - 50
downtime = downtime -.1
add(spell_book,
    spells[names(spells) %in% "Unseen Servant"])

gold = gold - scroll_p$`3` - 50*3
downtime = downtime -.1
add(spell_book,
    spells[names(spells) %in% "Leomund's Tiny Hut"])

# force is used as a noun
spell_book$`Leomund's Tiny Hut`$text = ""
```


### Final State

```{r}
assertthat::assert_that(gold>=0)
c(level = level,
  gold = gold,
  downtime = downtime,
  hp = hp)
ability_scores
skills
expertise
tools
```
```{r,results = 'asis'}
features %>%{cat(paste("- ",.),sep='\n')}
# magic item limit for tier 2: 3
magic_items %>% sort  %>%{cat(paste("- ",.),sep='\n')}
# common item limit for tier 2: 5
# common_items %>% sort  %>%{cat(paste("- ",.),sep='\n')}
# consumable limit for tier 2: 10
consumables %>% sort  %>% {cat(paste("- ",.),sep='\n')}
mundane_items %>% sort %>%{cat(paste("- ",.),sep='\n')}
```

```{r}
spell_book
available_elements(spell_book) %>% 
    {.[sapply(.,length)!=0]}
```